### 2023-07-18 Article_PySF.tex
myzhu update

        \texttt{move\_dip\_zero}    & Indicates whether to shift the molecular coordinates such that its dipole moment \cyan{[Eq.~(\ref{eq:ParentIonDipole})]} vanishes

>>>>

        \texttt{move\_dip\_zero}    & Indicates whether to shift the molecular coordinates such that the dipole moment of the parent ion \cyan{[Eq.~(\ref{eq:ParentIonDipole})]} vanishes
